Navigating to a greener Europe with 24/7 hourly carbon-free electricity procurement

### 2023-10-13 manuscript/sections/discussion.tex
discussion: add features text

These results highlight that voluntary commitments to 24/7 hourly matching goals can create an early market for the advanced technologies.

>>>>

\textbf{Features of 24/7~CFE not covered in this work --} Some positive features of 24/7 CFE procurement fall beyond the scope of this manuscript.

% on the impact on back up flexibility needs
From a system-wide benefits perspective, voluntary commitments to 24/7 CFE reduce the need for flexibility in background electricity systems. 
There will be less investment in gas-fired peaker generators, as well as less need for battery storage elsewhere in the system.
This effect has been explored in Xu et al. (2022) and Riepin~\&~Brown (2022) \cite{riepin-zenodo-systemlevel247,xu-247CFE-report}

% add a point on the price hedge
From an electricity buyer perspective, 24/7 CFE procurement can provide a hedge against volatile wholesale market prices.
Since 100\% CFE matching implies covering the entire electricity demand with clean energy from procured generators via power purchase agreements and operating storage, the buyer is not exposed to the wholesale market price risk (see \cref{fig:10-2025-IE-p1-used}).
More information on the price hedge effect is provided by the 24/7 CFE Energy Compact \cite{gocarbonfree247}.
